InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-23 paper.tex
back again

The first image generative model we use is the \textbf{Stable Diffusion} model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}. \newline
Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders. Due to its work directly in pixel space, they are very computational expensive. To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders. This works without losing quality and flexibility. \cite{Rombach_2022_CVPR}

As a second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}). OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream. This is achieved by training a transformer to autoregressively model those tokens into the resulting stream. \newline
This is done in two steps:

@@

We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning. \newline 
\cite{radford2018improving} try to avoid this problem in a simple two step procedure:

>>>>

The first image generative model we use is the \textbf{Stable Diffusion} model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.

Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders. Due to its work directly in pixel space, they are very computational expensive. To lower the computational costs, the Stable Diffusion model (v1.5) is applied in a latent space of powerful pretrained autoencoders. This works without losing quality and flexibility. \cite{Rombach_2022_CVPR}

As a second image generative model we use \textbf{OpenDalle} from dataautogpt3 (\url{https://huggingface.co/dataautogpt3/OpenDalle}). OpenDalle, as it is based on the Dall-E model, works by modelling text and image tokens as a single data stream. This is achieved by training a transformer to autoregressively model those tokens into the resulting stream.

This is done in two steps:

@@

We choose the \textbf{GPT2} model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.

\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
